% possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\documentclass[11pt,letterpaper,sans]{moderncv}

% moderncv themes
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{blue}
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% to set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% uncomment below to suppress automatic page numbering for CVs longer than one page
\nopagenumbers{}

% cover letter fixes
%\patchcmd{\makeletterclosing}{[3em]}{[3em]}{}{} % reduce space inbetween closing and name in cover letter

\patchcmd{\makeletterhead}{[1.5em]}{[0.75em]}{}{} % space between letter and opening

\patchcmd{\makeletterhead}{[2em]}{[1em]}{}{} % space between address and opening. actually is space between date and opening

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\patchcmd{\makecvtitle}{[b]}{[t]}{}{}
\patchcmd{\makecvtitle}{[b]}{[t]}{}{} % move name upwards
% adjust the page margins
\usepackage[scale=1, top=0.75in, bottom=.75in, left=0.75in, right=0.75in]{geometry}
\setlength{\hintscolumnwidth}{3.8cm}                % if you want to change the width of the column with the dates
\renewcommand*{\namefont}{\fontsize{28}{40}\mdseries\upshape} %change font size of title

% personal data
\name{Stephen}{Walker-Weinshenker}
%\title{Resume}                               % optional
\address{772 Ivy St}{Denver CO 80220}{} % optional
\phone[mobile]{+1~(720)~474~1422}                   % optional, "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[home]{+1~(303)~316~6757}
\email{resume@sww1235.net}                          % optional
%\homepage{www.johndoe.com}                         % optional
\social[linkedin]{Stephen Walker-Weinshenker}       % optional
%\social[twitter]{sww1235}                          % optional
\social[github]{sww1235}                            % optional
%\extrainfo{additional information}                 % optional
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file

% TODO: Reminder: use tags to separate resume versions

%https://tex.stackexchange.com/a/108909
\makeatletter
\newcommand*{\ccvitem}[3][.25em]{%
	\begin{tabular}{@{}m{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}m{\maincolumnwidth}@{}}%
		\raggedleft\hintstyle{#2} &{#3}%
	\end{tabular}%
	\par\addvspace{#1}}
\makeatother

%https://tex.stackexchange.com/a/86658
% the following definition is from the file moderncvstyleclassic.sty
\renewcommand*{\cventry}[7][.25em]{%
	\cvitem[#1]{#2}{%
	{\bfseries#3}%
%	\ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
	\ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% ... into this one (without comma).
	\ifthenelse{\equal{#5}{}}{}{, #5}%
	\ifthenelse{\equal{#6}{}}{}{ #6}%
	.\strut%
	\ifx&#7&%
	\else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}


\begin{document}

%TODO: note be sure to compile with make.sh or comment out, maybe fix with ifdef somehow

%\ifdefined\coverLetter{}
%	\input{\coverLetter}
%	\clearpage
%\else
%	\message{No cover letter output}
%\fi


%-----       resume       ---------------------------------------------------------
\restoregeometry{}
\makecvtitle{}

\vspace*{-1.3cm} % remove vertical space under title and name


\section{Professional Experience}

\cventry{2019--Present}{Distribution Automation/Communications Engineer}{Xcel Energy Inc}{Denver}{CO}{%
\begin{itemize}
	\item Assisted with Xcel's grid modernization efforts, including Advanced Metering and
		Field Area Network modernization with WiSUN and cellular modems.
	\item Supported Xcel's new Advanced Distribution Monitoring System deployment
		by establishing and troubleshooting communcations to field equipment.
	\item Developed islanding logic for new community scale microgrid implementations,
		including integration with battery and DER controllers.
	\item Engineered and standardized communication solution for Direct Transfer Trip implementation
		using high-speed radios and led standardization efforts for these projects.
	\item Co-developed and architected a device management database in Microsoft Access to allow multiple
		teams to efficiently share and work with device data.
	\item Developed the schema and data structure for the replacement of the MS Access database.
		The new schema is 3rd Normal Form compliant and mirrored the structure of other core
		company systems allowing easier integration between systems.
	\item Assisted with developing Xcel's Operational Technology security policies.
	\item Supported Downtown Network Monitoring deployment in Minnesota, including
		SCADA integration and testing.
	\item Developed and tested an integrated monitoring solution for MicroAT ATO controls using
		the Novatech Orion MX which allows for detection and notification of power outages on both feeders.
	\item Wrote several iterations of scripts allowing faster data import into Itron Gridscape.
	\item Rewrote and significantly expanded the Xcel Communications Standards Manual.
\end{itemize}
}

\cventry{2017--2019}{Area Engineering Intern}{Xcel Energy Inc}{Denver}{CO}{%
\begin{itemize}
	\item Improved field communications infrastructure for SCADA
		systems, including \newline radios and IP networks.
	\item Implemented new Field Area Network using WiMAX and WiSUN wireless technology.
	\item Performed field wireless propagation surveys to confirm chosen field locations would \newline communicate as designed.
\end{itemize}
}

%\cventry{2014--2019}{Lab Technician}{Engineering Network Services}{Fort
%Collins}{CO}{Supported computer labs for the College of Engineering at Colorado
%State University:
%\begin{itemize}
%	\item Maintained and installed Audio/Visual and computer hardware in computer labs.
%		Supported over 10 lab spaces and 240+ workstations.
%	\item Worked as part of a team managing computer operating system images and
%		software deployments in the engineering computer labs for 10 different \newline
%		engineering departments.
%	\item Supported over 400 lab users including students and professors.
%	\item Designed a low-cost projector remote control to eliminate IR interference issues
%		and battery replacements for lab spaces with multiple projectors.
%\end{itemize}
%}

\section{Certifications/Licenses}
\cvitem[0.75em]{March 2025}{Licensed as a Professional Engineer (PE) in Colorado: PE.0066180.}
\cvitem[0.75em]{May 2019}{Certified as Engineering Intern (EI) in Colorado.}
\cvitem[0.75em]{April 2015}{Amateur Radio License --- call sign KE0DZE.}

%\section{Professional Memberships}
%\cvitem{2015--Present}{Institute of Electrical and Electronics Engineers (IEEE).}

%\newpage

\section{Professional Skills}
\ccvitem[0.75em]{Distribution Automation}{Familiar with operation and troubleshooting of SCADA protocols including DNP3, Modbus and Mirrored Bits.}

\ccvitem[0.75em]{Distribution Automation}{Worked with multiple vendor's RTUs and RTACs, including SEL, S\&C and Eaton/Cooper.
	Proficient understanding of logic development for these platforms.}

\ccvitem[0.75em]{Distribution Automation}{Experience with distribution equipment such as RTACs, PLCs and
	Automation/Protection Controllers for Reclosers, Capacitor Banks,
	Automated Switchgear, Voltage Regulators and Source Transfer equipment.}

\ccvitem[0.75em]{Distribution Automation}{In-depth experience programming and troubleshooting Automated equipment
	using software such as S\&C Intellilink, SEL AcSELerator Quickset, SEL AcSELerator RTAC,
	Eaton Proview 5.0, Eaton Proview NXG, and Novatech NCD.}

\ccvitem[0.75em]{Radios and Communications}{Experience with troubleshooting and programming Itron WiSUN
	equipment including Access Points, Relays, Bridges and WiSUN NICs. Familar with
	the Itron UtilityIQ suite, especially the GridScape configuration tool.}

\ccvitem[0.75em]{Radios and Communications}{Extensive experience programming and troubleshooting cellular radios,
	including the RV50 series of cellular modems from Sierra Wireless/Semtech.}

\ccvitem[0.75em]{SCADA}{Familar with Schneider Electric ADMS SCADA platform, including troubleshooting
	device communcations and protocol configuration.}

\ccvitem[0.75em]{IT and Networking}{Experience troubleshooting at all layers of network stacks,
	including physical, TCP/IP and higher level protocols and using Wireshark protocol analyzer software.}

\ccvitem{IT and Networking}{Experience programming and troubleshooting network equipment including Ruggedcom switches and routers.}

\ccvitem[0.75em]{IT and Networking}{Familar with design and layout of networks for redundancy and efficiency. Specific experience
	with specific experience with the Ruggedcom Expanded Rapid Spanning Tree (xRSTP) protocol.}

\ccvitem[0.75em]{Mechanical Design}{Layout and design of equipment enclosures and mounting
	hardware for electrical equipment, antennas and cable supports.}

\ccvitem[0.75em]{Troubleshooting}{Skilled in troubleshooting electrical and communications equipment.}

\ccvitem[0.75em]{Documentation}{Skilled at writing technical documentation for both technical and \newline non-technical audiences.}

\ccvitem[0.75em]{Systems Security}{Knowledgeable about all aspects of security, including physical security and network security.
	Routinely interface with Xcel ESEM engineers around OT and network security of Automation and Communication Assets.}

%\ccvitem[0.75em]{Systems Integration}{Experienced with programming and physical
%		integration of automation controllers and automated devices.}
%\ccvitem[0.75em]{Electronics Design and Robotics}{Designed and built a remote controlled
%		vehicle, designed a small belt-mounted computer, as well as multiple other small
%		electronics projects.}

\section{Computer Skills}
\ccvitem[0.75em]{Operating Systems}{Proficient user of Windows, Linux, FreeBSD/OpenBSD and MacOS.}

\ccvitem[0.75em]{Operating Systems}{Proficient in systems administration of the above mentioned operating systems.
	These skills are practiced in a lab enviroment at home.}

\ccvitem[0.75em]{Programming/Scripting}{Intermediate knowledge of Visual Basic for Applications, Python, Rust and Bash.\newline
	Able to quickly familiarize myself with other programming languages as job requirements change.}

\ccvitem[0.75em]{eCAD}{Proficient in PCB design in KiCAD.}

\ccvitem[0.75em]{CAD}{Proficient in Nemetschek Vectorworks, Autodesk Revit and Autocad, FreeCAD and Dassault Systèmes SOLIDWORKS.}


\section{Education}
\cventry{May 2019}{Bachelor of Science in Electrical Engineering}{}{}{}{\textit{Colorado State University}, Fort Collins CO}


\end{document}
