% possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\documentclass[10pt,letterpaper,sans]{moderncv}

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{blue}
% to set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% uncomment below to suppress automatic page numbering for CVs longer than one page
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\patchcmd{\makecvtitle}{[b]}{[t]}{}{}
\patchcmd{\makecvtitle}{[b]}{[t]}{}{} % move name upwards
% adjust the page margins
\usepackage[scale=0.8, top=0.75in, bottom=.75in, left=0.75in, right=0.75in]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{15cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\renewcommand*{\namefont}{\fontsize{28}{40}\mdseries\upshape} %change font size of title

% personal data
\name{Stephen}{Walker-Weinshenker}
%\title{Resume}                               % optional
\address{8070 E. 26th Ave}{Denver CO 80238}{United States}% optional
\phone[mobile]{+1~(720)~474~1422}                   % optional, "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
\phone[home]{+1~(303)~316~6757}
\email{sww1235@gmail.com}                           % optional
%\homepage{www.johndoe.com}                         % optional
\social[linkedin]{Stephen Walker-Weinshenker}       % optional
%\social[twitter]{sww1235}                          % optional
\social[github]{sww1235}                            % optional
%\extrainfo{additional information}                 % optional
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file


\begin{document}

%-----       resume       ---------------------------------------------------------

\makecvtitle{}
\vspace*{-1.5cm} % remove vertical space under title and name

\section{Education}
%\cventry{2009--2013}{High School}{Denver Waldorf High School}{Denver}{\textit{Grade}}{Description}  % arguments 3 to 6 can be left empty
\cventry{2013--Present}{Electrical Engineering}{Colorado State University}{Fort Collins}{\textit{Junior}}{Anticipated completion date Spring 2018.\newline{}
Relevant courses completed by Summer 2017:
\vspace{-0.3cm}
\begin{multicols}{3}
\begin{itemize}
\item DC Circuit Analysis.
\item AC Circuit Analysis.
\item Digital Circuit Logic.
\columnbreak{}
\item Java Programming 1 \& 2.
\item Linear Systems Analysis 1 \& 2.
\columnbreak{}
\item Electronic Principles 1 \& 2.
\item Electromagnetic Fields 1 \& 2.
\end{itemize}
\end{multicols}
}

%\section{Master thesis}
%\cvitem{title}{\emph{Title}}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}

\section{Experience}
\subsection{Work}
\cventry{2014--Present}{Lab Technician}{Engineering Network Services}{Fort
Collins}{CO}{Supported computer labs for the College of Engineering at Colorado
State University.
\begin{itemize}
\item Worked as part of a team to support computer lab users.
\item Worked as part of a team to maintain and install hardware in computer labs.
\item Worked as part of a team managing computer operating system images and
software in labs
\end{itemize}
}

\subsection{Volunteering}
\cventry{2011--2014}{Intern}{Aurora Fox Arts Center}{Denver}{CO}{Volunteered as
a theatre lighting technician and stagehand during the summers. Designed
lighting for a show; worked as primary student electrician during the summers.}
\cventry{2014-Present}{Volunteer}{National Western Stock Show and
Rodeo}{Denver}{CO}{Volunteered in a variety of capacities, including assisting
with logistics for the kickoff parade.}

\vspace*{-.25cm}
\section{Computer Skills}
\cvitem{Windows}{Proficient in day to day usage as well as domain functionality.}
\cvitem{Mac}{Primary operating system used. Familiar with Unix underpinnings.}
\cvitem{Linux}{Proficient in *nix OSs.}
\cvitem{Programming/Scripting}{Basic knowledge of Java, Python, C, Golang and Bash.}
\cvitem{eCAD}{Proficient in Cadsoft Eagle and KiCAD.}
\cvitem{CAD}{Proficient in Nemetschek Vectorworks.}

\vspace*{-.4cm}
\section{Professional Memberships}
\cvitem{2015-Present}{Institute of Electrical and Electronics Engineers (IEEE)}

\vspace*{-.4cm}
\section{Activities}
\cventry{2015-Present}{President}{Hashdump: Colorado State University's
computer security club}{Fort Collins}{CO}{}
\cventry{2015--2016}{Secretary}{Hashdump: Colorado State University's computer
security club}{Fort Collins}{CO}{}
\cventry{2015-Present}{Participant}{Colorado State University Amateur Radio
Club}{Fort Collins}{CO}{}

\vspace*{-.4cm}
\section{Professional Interests/Skills}
\cvitem{Systems Security}{I enjoy learning about all aspects of security,
including physical security and network security. As a member of Hashdump, we
won second place at the Rocky Mountain Collegate Cyber Defense Competition in
Spring 2016.}
\cvitem{Systems Integration}{I enjoy learning how buildings and factory lines
work and creating proposals for how to make these systems work better. I am
interested in learning more about SCADA and PLCs.}
\cvitem{Designing Electronics and Robots}{Designed and built a remote controlled
 vehicle, designed a small belt-mounted computer, as well as several other small
 electronics projects.}
%\cvitem{Architecture}{I have created several designs of potential houses for myself.}



%\vspace*{-.4cm}
%\section{References}
%\cvitem{}{References provided upon request.}



\clearpage
\newgeometry{scale=.75}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment Team}{ }
\date{\today}
\opening{To Whom It May Concern:}
\closing{Sincerely,}
\enclosure[Enclosure]{Resum\'e}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle{}

I am seeking an electrical engineering internship for the summer of 2017.
Currently, I am a student at Colorado State University, majoring in Electrical
Engineering.

As an electrical engineering student, I can add insight and value to any project
I may work on. In addition to my course work, I work part-time at the College
of Engineering for Engineering Network Services. As a lab technician, I have
learned how to work as part of a team to complete both individual and group
projects.

I am self motivated and desire to learn new things. I taught myself how to
program and hook up Arduinos and other micro-controllers well before I would
have learned this in college. I also built an 1.5 ft x 2.5 ft remote controlled
car out of a desire to understand motor controllers and remote control and
battery technology.

You will find more information about my education and experience in my attached
resumé. I am happy to supply you with any completed coursework, list of job
duties, references or other documents if needed.

Thank you very much for considering me for an internship. I look forward to
talking with you further.

\makeletterclosing{}


\end{document}
